\titleformat{\chapter}{\centering\hei\xiaosanhao}{\chaptername}{0pt}{}
\renewcommand{\bibname}{参考文献}
\begin{thebibliography}{8}
\thispagestyle{fancy}
%\setlength{\bibitemsep}{1.5\baselineskip}
%\renewcommand{\bibfont}{\wuhao}
\bibitem{CN12} 中国互联网络信息中心. 第 29 次中国互联网络发展状况统计报告[R]. 2012.1.15.
\bibitem{gct} Google. Google Chart Tools[E]. https://developers.google.com/chart/. Mar 26, 2012.
\bibitem{hashtag} Wikipedia. Hashtag[E]. http://en.wikipedia.org/wiki/Hashtag. Apr 23, 2013.
\bibitem{bigquery} Google. Google BigQuery[E]. https://developers.google.com/bigquery/. Jan 19, 2013.
\bibitem{json} Douglas Crockford. The application/json Media Type for JavaScript Object Notation (JSON)[E]. http://www.ietf.org/rfc/rfc4627.txt?number=4627. July, 2006.
\bibitem{d3} Michael Bostock, Vadim Ogievetsky, Jeffrey Heer. D3: Data-Driven Documents[J]. IEEE Transactions on Visualization and Computer Graphics archive. December 2011, 
Volume 17 Issue 12: Pages 2301-2309.
\bibitem{haixin13} MA H, QIAN W, XIA F, et al. Towards Modeling Popularity of Microblogs[J]. Frontiers of Computer Science. April 2013, Volume 7, Issue 2: pp 171-184.
\bibitem{perception} William S. Clevelanda, Robert McGilla. Graphical Perception: Theory, Experimentation, and Application to the Development of Graphical Methods[J]. Journal of the American Statistical Association. 1984, Volume 79, Issue 387: pages 531-554.
\bibitem{ekman71} Ekman, Paul; Friesen, Wallace V. Constants across cultures in the face and emotion[J].
Journal of Personality and Social Psychology. Feb 1971,  Vol 17(2): 124-129.
\bibitem{gpoms11} Bollen, J., Mao, H., Zeng, X.-J. Twitter mood predicts the stock market[J]. Journal of Computational Science. 2011, Volumn 2, Issue 1: pp. 1-8 
\bibitem{zj05} 钟杰，钱铭怡. 中文情绪形容词检测表的编制与信效度研究. 《中国临床心理学杂志》. 2005年, 第1期: 9-13页.
\bibitem{mr04} J. Dean and S. Ghemawat. MapReduce: Simplified Data Processing on Large Clusters[C]. OSDI 2004, San Francisco, CA, USA, 2004.
\bibitem{hdfs10} Konstantin Shvachko, Hairong Kuang, Sanjay Radia, and Robert Chansler, The Hadoop Distributed File System[C]. MSST 2010, Incline Village, NV, May 3-7, 2010.
\bibitem{dremel} Sergey Melnik, Andrey Gubarev, Jing Jing Long, Geoffrey Romer, Shiva Shivakumar, Matt Tolton, Theo Vassilakis. Dremel: Interactive Analysis of Web-Scale Datasets[C]. VLDB 2010, Singapore, 2010.

\bibitem{hadoop12}  Tom White. Hadoop: The Definitive Guide[M]. USA: O'Reilly Media, 2012.5.27.
\bibitem{jsgood} Douglas Crockford. JavaScript: The Good Parts[M]. USA: O'Reilly Media, 2008.8.
\bibitem{ajax} Anthony T. Holdener III. Ajax: The Definitive Guide[M]. USA: O'Reilly Media, 2008.1.15.
\bibitem{gae} Dan Sanderson. Programming Google App Engine[M]. USA: O'Reilly Media, 2012.10.26.
\bibitem{jquery} David Flanagan. jQuery Pocket Reference[M]. USA: O'Reilly Media, 2010.12.
\bibitem{jquery-ui} Eric Sarrion. jQuery UI[M]. USA: O'Reilly Media, 2012.3.
\bibitem{d3-book} Scott Murray. Interactive Data Visualization for the Web[M].  USA: O’Reilly Media, 2013.3.
\bibitem{http} David Gourley, Brian Totty, Marjorie Sayer, Anshu Aggarwal, Sailu Reddy. HTTP: The Definitive Guide[M]. USA: O'Reilly Media, 2002.9.
\bibitem{database} Abraham Silberschatz, Henry F. Korth, S. Sudarshan. Database System Concepts, Sixth Edition[M]. USA: McGraw-Hill. 2010.
\bibitem{servlet} Jason Hunter. Java Servlet Programming, 2nd Edition[M]. USA: O'Reilly Media, 2001.4.
\end{thebibliography}

